\documentclass[a4paper,12pt]{article}
\input{structure.tex} % Input the structure.tex file which specifies the document layout and style

%----------------------------------------------------------------------------------------

\begin{document}

\begin{center}
{\Huge How to use the Superuser interface}
\end{center}


%----------------------------------------------------------------------------------------
%	OVERVIEW SECTION
%----------------------------------------------------------------------------------------
\section{Overview}

The Superuser Interface allows easy creation of new configurations which the game can use.
The different types of configurations include:
\begin{itemize}
	\item New carriable items (medicine, food, etc.)
	\item New conditions (diabetes, renal failure etc.)
	\item New status effects that are linked to conditions (Blood Sugar etc)
	\item New customization items (new avatar items or house items)
	\item New mini-games the users can play
\end{itemize}

The purpose of the interface is to both allow quick access to the addition and removal of the objects without
direct access to the server, but also to allow those without the technical knowledge to navigate the server the
ability to still add their own ideas.


\section{Connecting}

Accessing the Superuser Interface is extremely simple: just add "/superuser.html" to the end of the address of the application and load that page. You will then be required to login (using details that should have been provided separately). This will give you access to the interface.

%----------------------------------------------------------------------------------------
%	THE SUPERUSER API SECTION
%----------------------------------------------------------------------------------------
\section{The Superuser API}
\subsection*{Add carriable}
This adds a new carriable item that users can add to the backpack.\\
Parameters:
\begin{itemize}
	\setlength\itemsep{0em}
	\item Name: The name of the item as it appears in game
	\item Sprite: The image the carriable displays in game. Must be PNG format.
	\item Effects: A list of effects this item has and how much it affects them by.
\end{itemize}

\subsection*{Remove carriable}
Deletes a carriable item from the game so users can no longer use it. A picture of the currently
selected item appears for confirmation.\\
Parameters:
\begin{itemize}
	\setlength\itemsep{0em}
	\item Name: Name of the currently selected carriable to be submitted for deletion
\end{itemize}

\newpage

\subsection*{Add status}
Adds a new status configuration. A status is what is affected by a condition.\\
e.g. Blood Sugar is a status, which is caused by the condition diabetes.\\
Parameters (all numbers must be integers):
\begin{itemize}
	\setlength\itemsep{0em}
	\item Name: the name of the status effect
	\item Min value: The minimum value the status can take (like "health value" of the status).
	\item Max value: The maximum value the status effect can take
	\item Healthy min value: The minimum value this status can take and still be considered healthy
	\item Healthy max value: The maximum value this status can take and still be considered healthy
	\item Sprite file: The sprite to use when the value is in an unhealthy range (showing the symptoms)
\end{itemize}

\subsection*{Remove status}
Removes the submitted status configuration file.
Parameters:
\begin{itemize}
	\setlength\itemsep{0em}
	\item Status: The status currently selected that if submitted, will be deleted.
\end{itemize}

\subsection*{Add condition}
Adds a new condition that users can have when they signup/change their conditions.
A condition is the medical condition such as diabetes or renal failure.
Note that you must specify the statuses that are related to this condition, and therefore you must create the statuses
first, and then create the condition.
Parameters:                                                                                                                                                                       
\begin{itemize}
	\setlength\itemsep{0em}
	\item Name: the name of the condition
	\item Statuses: the list of all the statuses associated with this condition
\end{itemize}

\subsection*{Remove condition}
Remove a condition so that users cannot select it.\\
Parameters:                                                                                                                                                                       
\begin{itemize}
	\setlength\itemsep{0em}
	\item Name: the name of the condition to be deleted
\end{itemize}

\subsection*{Add store item}
Adds a new item available to buy from the in-game store. These items include avatar items and hub customization items.\\
Parameters:
\begin{itemize}
	\setlength\itemsep{0em}
	\item Name: the name of the new item
	\item Description: a description of the item
	\item Slot: the slot this item is for
	\item Price: the price of the item. An item with price 0 will automatically be unlocked for all users
	\item Sprite: the image the item has in game. Must be PNG format.
\end{itemize}	

\subsection*{Remove store item}
Removes an item from the store. These items include avatar items and hub customization items.\\
Parameters:
\begin{itemize}
	\setlength\itemsep{0em}
	\item Slot: the slot of the item you want to remove
	\item Item: the name of the item  to be removed
\end{itemize}	

\subsection*{Add mini-game}
Adds a new mini-game to the server, so that users can play it.\\
Currently not implemented through the interface.\\

\subsection*{Remove mini-game}
Removes a mini-game from the server, so that users can no longer play it.
Parameters:
\begin{itemize}
	\setlength\itemsep{0em}
	\item Name: the name of the mini-game to delete
\end{itemize}		

\end{document}